---
title: "Gov1005: Problem Set 2"
author: "Rebecca Xi"
date: "2/12/2020"
output: html_document
---

```{r setup 1, include=FALSE}

# I had to install httr first (install.packages("httr")) in order to overcome
# the returned warning messages and install the other packages

library(dplyr)
library(fivethirtyeight)
library(tidyverse)
```

## Mad Libs

```{r Mad Lib 1, include=FALSE}

# slice(1) conveniently grabs the first entry of the selected and ordered column

r1 <- endorsements_2020 %>% 
  arrange(date) %>%
  select(date) %>%
  slice(1)
```

1. The earliest date for an endorsement in the dataset is `r r1`.


```{r Mad Lib 2, include=FALSE}

# We use desc() so that the first entry of the column is the most recent date,
# rather than the earliest

r2 <- endorsements_2020 %>% 
  arrange(desc(date)) %>%
  select(date) %>%
  slice(1)
```

2. The most recent date for an endorsement is `r r2`.


```{r Mad Lib 3, include=FALSE}

# filter() is useful for imposing the conditions we want on the dataset in
# question

r3 <- endorsements_2020 %>%
  filter(endorsee == "Pete Buttigieg", position == "mayor") %>%
  select(endorser)
```

3. `r r3` is the mayor that has endorsed Pete Buttigieg.


```{r Mad Lib 4, include=FALSE}

# Use summarize to average all values in the filtered and selected column
 
r4 <- endorsements_2020 %>% 
  filter(state == "NH") %>% 
  select(points) %>%
  summarize(mean_points = mean(points))
```

4. Endorsers from New Hampshire have an average of `r r4` endorsement points.


```{r Mad Lib 5, include=FALSE}

# filter() allows you to select for multiple values. As before, use summarize()
# to find the sum of all values in the filtered and selected column.

r5 <- endorsements_2020 %>%
  filter(endorsee == "Amy Klobuchar" | endorsee == "Elizabeth Warren") %>% 
  select(points) %>% 
  summarize(sum(points))
```

5. Between them, the two female candidates who remain in the race 
(Amy Klobuchar and Elizabeth Warren) have a total of `r r5` endorsement points.


6. The type of data you are working with (words, numbers, categories, or 
fancier data types like dates) determines what kinds of operations you can 
perform on it. To distinguish different types of data, it’s useful to use 
the function class(). This function allows you to get to know what kind of 
data you’re working with.

```{r Mad Lib 6a, include=FALSE}

# Since the class() function prints the vector of the names of classes an object
# inherits from - in this case, only one - you can simply assign the function
# result to a new variable. Syntax was found at
# https://davidkane9.github.io/PPBDS/4-wrangling.html.

aclass <- class(endorsements_2020$position)
```

    a. The variable “position” is a `r aclass` class of variable.


```{r Mad Lib 6b, include=FALSE}

# As before, simply assign the result of class() to a new variable

bclass <- class(endorsements_2020$endorser)
```

    b. The variable “endorser” is a `r bclass` class of variable.


```{r Mad Lib 6c, include=FALSE}

# As before, assign the result of class() to a new variable. We expect a
# different class type due to the nature of "points".

cclass <- class(endorsements_2020$points)
```

    c. The variable “points” is a `r cclass` class of variable.


## Put It Into Practice

```{r setup 2, include=FALSE}

# Remember to load gov.1005.data package, which was previously installed
# Remember to install and load ggthemes to use in my ggplot code chunk

library(gov.1005.data)
library(ggthemes)
```

```{r fivethirtyeight data, include=FALSE}

# We only care about the Democrat and Republican values, so we filter for those.
# We also only care about plotting year vs. average age, for each of the two
# parties, so we use group_by() and summarize() to get those variables in
# preparation for plotting.

age_data <- congress %>% 
  filter(party %in% c("D", "R")) %>% 
  group_by(year, party) %>% 
  summarize(avg_age = mean(age))
```

```{r fivethirtyeight graph, echo=FALSE}

ggplot(age_data, aes(x = year, y = avg_age, color = party)) +
  geom_line() +
  
# I used scale_color_manual() to manually assign the colors for the two party
# lines and used labs() to create a title, subtitle, and caption.

  scale_color_manual(values = c("D" = "blue", "R" = "red")) +
  labs(
    title = "Average Age of Members of Congress",
    subtitle = "At start of term, 1947-2013",
    caption = "Source: fivethirtyeight package"
  ) +
  
# In scale_x_continuous() and scale_y_continuous(), I defined the limits of the
# axes, axis breaks for each, and then any necessary axis tick labels. I ended
# up manually labeling the x-axis ticks, though I'm sure there are more
# efficient ways to do this. The only necessary y-axis tick label was "60 years"
# on the highest tick.
  
  scale_x_continuous(
    limits = c(1945, 2015),
    breaks = seq(1950, 2010, by = 10),
    labels = c(
      "1950" = "1950",
      "1960" = "'60", 
      "1970" = "'70",
      "1980" = "'80",
      "1990" = "'90",
      "2000" = "2000",
      "2010" = "'10")
  ) +
  scale_y_continuous(
    limits = c(40, 60), 
    breaks = seq(40, 60, by = 5),
    labels = c(seq(40, 55, by = 5), "60 yrs")
  ) + 
  
# Adding annotations to the two lines on the graph was straightforward, keeping
# in mind the colors already manually assigned to the two parties
  
  annotate("text", x = 1960, y = 57, label = "Republicans", color = "red") +
  annotate("text", x = 1995, y = 57, label = "Democrats", color = "blue") +
  
# An online introduction to the ggthemes package was helpful in discovering the
# fivethirtyeight theme. I also wanted to get rid of the legend on the right
# hand side, hence the use of legend.position = "none".
  
  theme_fivethirtyeight() +
  theme(legend.position = "none") 
```


### Colleagues:

* Grace Pan

* John Morse

* Rachel Auslander

* Will Scherpferman


